---
title: "GitHub Commit and Branch Example"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
    toc_depth: 2
---

# First Commit

This section represents the **first commit** of your project.

Typical contents:
- Initial project setup
- Adding `.gitignore`
- Creating a basic `README.md`
- Initializing Git with `git init`

```{r first-commit-example, eval=FALSE}
# Terminal commands
mkdir my-project
cd my-project
git init
echo "# My Project" > README.md
git add .
git commit -m "Initialize project with basic structure"
```

---

# Second Commit

This section corresponds to your **second commit**, where you add your R Markdown file and test output.

```{r second-commit-example, eval=FALSE}
# Add example R Markdown file
touch example_github_doc.Rmd

# Stage and commit
git add example_github_doc.Rmd
git commit -m "Add example R Markdown file for GitHub document output"
```

---

# Branches

You can create and test changes safely in separate branches.

```{r branch-example, eval=FALSE}
# Create and switch to a test branch
git checkout -b test-doc-output

# Make changes, then commit
git add .
git commit -m "Test rendering of R Markdown output"

# Merge back to main when ready
git checkout main
git merge test-doc-output
```

**Common branch names:**
- `main` → stable production branch  
- `test-doc-output` → for testing `.Rmd` output  
- `feature-rmd-template` → for adding R Markdown features  

---

# Summary

This R Markdown file demonstrates:
- How to structure commits in a Git project  
- How to use branches for testing  
- How to document your workflow in a GitHub-ready format
